Postural developments mediate children's visual access to social information

### 2018-01-28 writeup-cogsci/cogsci2018_faceOnly.Rmd
new banner

\begin{figure*}
\includegraphics[width=6in]{images/framesample.pdf}
\caption{\label{fig:frames} Example face detections made by MTCNN for the headcam videos from a child in each group  (green squares).}
\end{figure*}

>>>>

\begin{figure*}
\includegraphics[width=6in]{images/detector_samples_banner.pdf}
\caption{\label{fig:frames} Example face and pose detections made by OpenPose (top row) and MTCNN (bottom row) from a child in each age group. The last column features a false positive from OpenPose and a false negative from MTCNN.}
\end{figure*}

### 2018-01-28 writeup-cogsci/cogsci2018_faceOnly.tex
new banner

To evaluate detector performance, we constructed a ``gold set'' of
frames by hand labeling both a sample of frames with a high density of
faces (half reported by the MTCNN, half by OpenPose) and a random sample
from the remaining frames; each sample was comprised of frames sampled
from each participant (i.e., video). This was done so as to not bias our
evaluation by the relatively rare appearance of faces in the dataset.
Faces were classifed as present in a frame if at least half of the face
was showing. Precision (hits / hits + false alarms), recall (hits / hits
+ misses), and F-score (harmonic mean of previous measures) were
calculated for all detectors and are reported in Table 2.

Both OpenPose and MTCNN detectors performed relatively well on the gold
set, with MTCNN outperforming OpenPose on the random sample but trailing
behind in the high density sample. We found a clear tradeoff between
recall and precision between the two models. That is, MTCNN almost
always detected a face if it was present, but made more false alarms;
conversely, OpenPose made less false alarms but overall detected fewer
faces. ViolaJones performed quite poorly, missing many of the faces in
the randomly sampled frames.

@@

To formalize these observations, we fit a generalized logistic
mixed-effect model to all with the presence/absence of a face on every
frame (as detected by MTCNN), with participant's age, orientation, and
posture as predictors. Interactions between predictors were not included
as this maximal model failed to converge. A summary of the coefficients
of this model can be found in Table 3. While age remained a significant
predictor even when accounting for the effects of infants' posture and
orientation, it accounted for the least amount of variance. Overall,
these results suggest that, instead, infants' access to faces is heavily
infleunced by their own posture and their orientation towards their
caregiver. We found the same pattern of results for the OpenPose
detections, omitted here for brevity.

@@

\subsection{Access to Faces During Labeling
Events}\label{access-to-faces-during-labeling-events}

Finally, we analyzed how face detections changed during object labeling
events as a function of infant's posture and orientation. Specfically,
we analyzed a four-second window around each labeling event (e.g.,
``Look at the {[}zem{]}!''); these labeling events were hand-annotated
and automatically synchronized with the frame-by-frame face detections.
We again found that infant's posture impacted the degree to which they
saw their caregiver's face during a labeling event; infants who were
sitting or standing were more likely to have access to their caregiver's
face.

@@

We use a head-mounted camera to explore how children's postural and
locomotive development directly impacts their access to social
information relevant for word-learning, here operationalized as the
presence of the faces of their caregiver. We found that children's
posture and orientation towards their caregiver changed systematically
across age, and that all three of these factors dramatically impacted
the proportion of faces that were avaliable in the child's visual field.
Thus, infants' postural development is a mediating factor that explains
age-related changes in the proportion of faces avaliable in infants'
visual field.

>>>>

To evaluate face detector performance, we constructed a ``gold set'' of
frames by hand labeling both a sample of frames with a high density of
faces (half reported by the MTCNN, half by OpenPose) and a random sample
from the remaining frames; each sample was comprised of frames sampled
from each participant (i.e., video). This was done so as to not bias our
evaluation by the relatively rare appearance of faces in the dataset.
Faces were classifed as present in a frame if at least half of the face
was showing. Precision (hits / hits + false alarms), recall (hits / hits
+ misses), and F-score (harmonic mean of previous measures) were
calculated for all detectors and are reported in Table 2. For wrist
detections, the ``gold set'' was constructed in the same way, except
that frames with a high density of wrists were taken by wrist detections
made by OpenPose.

For face detectionm, both OpenPose and MTCNN detectors performed
relatively well on the gold set, with MTCNN outperforming OpenPose on
the random sample but trailing behind in the high density sample. We
found a clear tradeoff between recall and precision between the two
models. That is, MTCNN almost always detected a face if it was present,
but made more false alarms; conversely, OpenPose made less false alarms
but overall detected fewer faces. ViolaJones performed quite poorly,
missing many of the faces in the randomly sampled frames. Overall, MTCNN
had a slightly higher f-score (f = 0.89) than OpenPose (f = 0.83); for
brevity, we thus report analyses only using these detector outputs
(though we found the same pattern of results; anlayses code avaliable at
\url{https://github.com/amsan7/xs-face}).

For wrist detection, OpenPose performed moderately well (f = 0.72) with
relatively high precision, but low recall on the randomly sampled set of
frames (see Table 2). We thus analyze wrist detections, with the caveat
that we are likely underestimating the proportion of wrists overall in
the datatset.

@@

To formalize these observations, we fit a generalized linear model to
the proportion faces infants saw in each posture and orientation (as
detected by MTCNN), with participant's age, orientation, and posture as
independent variables. A summary of the coefficients of a model with
only main effects (and no interactions) model can be found in Table 3.
When we did include interaction terms between age, posture, and
orientation, age no longer remained a significant predictor (b = -15.84,
SE = 113.98, z = -0.14 , p =0.89). We found the same pattern of results
for the OpenPose face detections, omitted here for brevity. We also
found the same pattern with respect to infant's visual access to hands
(see Table 4); including interaction terms also reduced any main effect
of age on the proportion of hands detected (b = -15.7, SE = 113.98, z =
-0.14 , p =0.89). Thus, these results suggest that infants access to
social information is heavily infleunced by their postural and
locomotive development.

@@

\subsection{Access to Faces and Wrists During Labeling
Events}\label{access-to-faces-and-wrists-during-labeling-events}

Finally, we analyzed how face and wrists detections changed during
object labeling events as a function of infant's posture and
orientation. Specfically, we analyzed a four-second window around each
labeling event (e.g., ``Look at the {[}zem{]}!''); these labeling events
were hand-annotated and automatically synchronized with the
frame-by-frame face detections. We again found that infant's posture and
orientations impacted the degree to which they saw their caregiver's
face and wrist during a labeling event; infants who were sitting or
standing were more likely to have access to this social information.

@@

We use a head-mounted camera to explore how children's postural and
locomotive development directly impacts their access to social
information, here operationalized as the presence of the faces and
wrists of their caregiver. We found that children's posture and
orientation towards their caregiver changed systematically across age,
and that both of these factors dramatically impacted the proportion of
faces and wrists that were avaliable in the child's visual field. Thus,
infants' postural and locomotive developments are mediating factors that
explain some of the age-related changes in the proportion of faces and
hands avaliable in infants' visual field. Broadly, this work suggests
that motoric developments mediate how infants experience their visual
world and the social information in it: infants that are sitting and
standing have a different view of their world, the people in it, and the
actions that are being performed.
